Differentially Private Bayesian Inference

### 2018-02-16 main.tex
update macros file

\section{Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\mathsf{BayesInfer}(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\mathsf{BayesInfer}(x)$.

@@

\subsubsection{Mechanism Set up}
In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
R = \{\mathsf{BayesInfer}(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

Hellinger distance $\mathsf{Hlg}$ is used here to score these candidates. The utility function:
\begin{equation}
\label{equ_utility}
u(x,r) = -\mathsf{Hlg}(\mathsf{BayesInfer}(x), r); r \in R.
\end{equation}

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{multline*}
\Delta_{g}u = 
\mathsf{Hlg}(\mathsf{BayesInfer}(x'), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|\\
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\end{multline*}

% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$. Since $\mathsf{Hlg}$ is monotonic, i.e. our utility function is monotonic.

\subsubsection{Security Analysis}
It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\mathsf{BayesInfer}$ with privacy mechanism as $\mathsf{PrivInfer}$. For adjacent data set $||x,y||_1 = 1$:
\begin{equation*}
\begin{split}
& \frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \\
& =\frac
{\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
{\frac
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
& = \left(\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
\right)
\cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp\left(\frac
{\epsilon (u(x,r) - u(y,r))}
{2 \Delta_{g}u}
\right) \\
& \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& \leq
exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp(\epsilon).
\end{split}
\end{equation*}

@@

\begin{multline*}
\Delta_{l}u(x) = 
\mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|\\
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\end{multline*}

@@

From Eq. \ref{equ_utility}, $\{u(x,r') \leq 0|r' \in R\}$ and $\{u(y,r') \leq 0|r' \in R\}$, we can infer that $r = arg(\max\limits_{r \in R}\{u(x,r')\}) = \mathsf{BayesInfer}(x)$ and $u(x,r) = 0$.From $\Delta_{l}u(y) = u(x,r) - u(y,r)$, we can also infer that $\Delta_{l}u(y) = - u(y,r)$. Then, the following relationship between $u(x,r)$, $u(y,r)$, $\Delta_{l}u(x)$ and $\Delta_{l}u(y)$:
\begin{equation*}
\begin{split}
- \Delta_{l}u(x) & < \Delta_{l}u(y) \\
\Delta_{l}u(x) - \Delta_{l}u(y) & < 2 \Delta_{l}u(x) \\
- \Delta_{l}u(y) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
u(y,r) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} & > 2.
\end{split}
\end{equation*}

@@

$x_0$ to denote:
\begin{small}
\begin{equation*}
\begin{split}
&\mathsf{if}\ n\ is\ even\\
&\mathsf{then}\ \mathsf{BayesInfer}(x_0) = beta(\frac{n}{2} + 1, \frac{n}{2} + 1)\\
&\mathsf{else}\ \mathsf{BayesInfer}(x_0) = \{beta(\frac{n+1}{2} + 1, \frac{n-1}{2} + 1),\\
&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad beta(\frac{n - 1}{2} + 1, \frac{n + 1}{2} + 1)\}
\end{split}
\end{equation*}
\end{small}

@@

Then, we have the following three statements, and proofs of the statements.
\renewcommand{\labelenumi}{\Roman{enumi}}
\begin{enumerate}
\item $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\ \forall x \geq x_0$;

or $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) > \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\forall x \leq x_0$.

\item $\Delta_{l}u(x) = \mathsf{Hlg} (\mathsf{BayesInfer}(x),\mathsf{BayesInfer}(x + 1)),\forall x \geq x_0$;

$\Delta_{l}u(x) = \mathsf{Hlg} (\mathsf{BayesInfer}(x),\mathsf{BayesInfer}(x - 1)),\forall x \leq x_0$.

@@

\begin{proof}
Since the Hellinger distance is symmetric, if we prove the $\mathsf{Hlg} (\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x + 1), \mathsf{BayesInfer}(x + 2))\ \forall x \geq x_0$, the other part when $\forall x \leq x_0$ also holds.

1. if $x = x_0$, $\mathsf{Hlg} (\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 + 1)) < \mathsf{Hlg} (\mathsf{BayesInfer}(x_0 + 1), \mathsf{BayesInfer}(x_0 + 2))$ holds:

% \twocolumn{
\begin{equation*}
\boxed{
\begin{split}
\mathsf{Hlg}(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \mathsf{Hlg}(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\mathsf{beta}(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\mathsf{beta}(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
}
\end{equation*}

@@

i.e $\mathsf{Hlg}(beta(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m), beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1)) 
< \mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2))$
is what we know:

@@

Now, we need to proof $\mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2)) 
< \mathsf{Hlg}(beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2), beta(\frac{n}{2} + 1 + m + 3, \frac{n}{2} + 1 - m - 3))$ by using what we know.

@@

\begin{equation*}
\begin{split}
& \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
> & \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
& \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
< & \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
& \mathsf{Hlg}(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
< & \mathsf{Hlg}(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{footnotesize}

@@

\begin{equation*}
\begin{split}
\because \quad 		& \Delta_l u(x) = |\mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)|,\\
					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
\because \quad 		& \mathsf{Hlg}(\mathsf{BayesInfer}(x), r) - \mathsf{Hlg}(\mathsf{BayesInfer}(y'), r)\\
					& \leq \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(y'));\\
\therefore \quad 	& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(y')),\\
					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
\therefore \quad 	& \Delta_l u(x) = \max \{\mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)),\\
					& \quad \quad \quad \quad \quad \quad \quad \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\};\\
					& According\ to\ Statement\ I:\\
\mathsf{if}	  \quad	& x > x_0 \\
\mathsf{then} \quad	
					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\\
					&< \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1));\\
\mathsf{then} \quad	
					& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1));\\
\mathsf{if}	 \quad	& x < x_0 \\
\mathsf{then} \quad	
					& \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1))\\
					& > \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x + 1)); \\
\mathsf{then} \quad	
					& \Delta_l u(x) = \mathsf{Hlg}(\mathsf{BayesInfer}(x), \mathsf{BayesInfer}(x - 1));\\
\mathsf{else} \quad	
					& \Delta_l u(x_0) = \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 - 1))\\
					& \quad \quad \quad = \mathsf{Hlg}(\mathsf{BayesInfer}(x_0), \mathsf{BayesInfer}(x_0 + 1)). \\
\end{split}
\end{equation*}

>>>>

\section{Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

@@

\subsubsection{Mechanism Set up}
In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
R = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
\begin{equation}
\label{equ_utility}
u(x,r) = -\hlg(\bysinfer(x), r); r \in R.
\end{equation}

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{multline*}
\Delta_{g}u = 
\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|\\
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\end{multline*}

% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$. Since $\hlg$ is monotonic, i.e. our utility function is monotonic.

\subsubsection{Security Analysis}
It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\mathsf{PrivInfer}$. For adjacent data set $||x,y||_1 = 1$:
\begin{equation*}
\begin{split}
& \frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \\
& =\frac
{\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
{\frac
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
& = \left(\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
\right)
\cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp\left(\frac
{\epsilon (u(x,r) - u(y,r))}
{2 \Delta_{g}u}
\right) \\
& \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& \leq
exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp(\epsilon).
\end{split}
\end{equation*}

@@

\begin{multline*}
\Delta_{l}u(x) = 
\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\\
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\end{multline*}

@@

From Eq. \ref{equ_utility}, $\{u(x,r') \leq 0|r' \in R\}$ and $\{u(y,r') \leq 0|r' \in R\}$, we can infer that $r = arg(\max\limits_{r \in R}\{u(x,r')\}) = \bysinfer(x)$ and $u(x,r) = 0$.From $\Delta_{l}u(y) = u(x,r) - u(y,r)$, we can also infer that $\Delta_{l}u(y) = - u(y,r)$. Then, the following relationship between $u(x,r)$, $u(y,r)$, $\Delta_{l}u(x)$ and $\Delta_{l}u(y)$:
\begin{equation*}
\begin{split}
- \Delta_{l}u(x) & < \Delta_{l}u(y) \\
\Delta_{l}u(x) - \Delta_{l}u(y) & < 2 \Delta_{l}u(x) \\
- \Delta_{l}u(y) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
u(y,r) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} & > 2.
\end{split}
\end{equation*}

@@

$x_0$ to denote:
\begin{small}
\begin{equation*}
\begin{split}
&\mathsf{if}\ n\ is\ even\\
&\mathsf{then}\ \bysinfer(x_0) = beta(\frac{n}{2} + 1, \frac{n}{2} + 1)\\
&\mathsf{else}\ \bysinfer(x_0) = \{beta(\frac{n+1}{2} + 1, \frac{n-1}{2} + 1),\\
&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad beta(\frac{n - 1}{2} + 1, \frac{n + 1}{2} + 1)\}
\end{split}
\end{equation*}
\end{small}

@@

Then, we have the following three statements, and proofs of the statements.
\renewcommand{\labelenumi}{\Roman{enumi}}
\begin{enumerate}
\item $\hlg (\bysinfer(x), \bysinfer(x + 1)) < \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\ \forall x \geq x_0$;

or $\hlg (\bysinfer(x), \bysinfer(x + 1)) > \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\forall x \leq x_0$.

\item $\Delta_{l}u(x) = \hlg (\bysinfer(x),\bysinfer(x + 1)),\forall x \geq x_0$;

$\Delta_{l}u(x) = \hlg (\bysinfer(x),\bysinfer(x - 1)),\forall x \leq x_0$.

@@

\begin{proof}
Since the Hellinger distance is symmetric, if we prove the $\hlg (\bysinfer(x), \bysinfer(x + 1)) < \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\ \forall x \geq x_0$, the other part when $\forall x \leq x_0$ also holds.

1. if $x = x_0$, $\hlg (\bysinfer(x_0), \bysinfer(x_0 + 1)) < \hlg (\bysinfer(x_0 + 1), \bysinfer(x_0 + 2))$ holds:

% \twocolumn{
\begin{equation*}
\boxed{
\begin{split}
\hlg(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \hlg(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\mathsf{beta}(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\mathsf{beta}(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
}
\end{equation*}

@@

i.e $\hlg(beta(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m), beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1)) 
< \hlg(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2))$
is what we know:

@@

Now, we need to proof $\hlg(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2)) 
< \hlg(beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2), beta(\frac{n}{2} + 1 + m + 3, \frac{n}{2} + 1 - m - 3))$ by using what we know.

@@

\begin{equation*}
\begin{split}
& \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
> & \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
& \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
< & \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
& \hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{footnotesize}

@@

\begin{equation*}
\begin{split}
\because \quad 		& \Delta_l u(x) = |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)\\
					& \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
\therefore \quad 	& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(y')),\\
					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)),\\
					& \quad \quad \quad \quad \quad \quad \quad \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
					& According\ to\ Statement\ I:\\
\mathsf{if}	  \quad	& x > x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
					&< \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{if}	 \quad	& x < x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
					& > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x - 1));\\
\mathsf{else} \quad	
					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1))\\
					& \quad \quad \quad = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
\end{split}
\end{equation*}
